Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-12 popl24/composition.tex
checkpoint

Our certification techniques are defined generally wrt implementations
of input encoding, decoding, and internal gates for both GMW and YGC
circuits. In the following we will refer to arbitrary decode, encode,
and gate functions with the restriction that any function in each of
these categories has the same valid type signatures as their existing
instantiations in our GMW and YGC libaries. All certifications can be
automatically verified as a consequence of Lemmas \ref{lemma-cprogtt}
and \ref{lemma-autosep}, and complete implementations of the
certifications are available in our repository \cite{jpdf-github}.

We also demonstrate that intenstional properties of certified
components maintain a crucial separation invariant within circuits
using methods developed in Section \ref{section-automation-logic}.
Specifically, we show that within a circuit $\prog$, the views of each
client remain probabilistically independent of the other client's
secrets, i.e., $\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
%\quad \text{and} \quad
$\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$.
Through certification of decodings we can finally obtain $\NIMO$ in
circuits as in Theorems \ref{theorem-gmw-NIMO} and
\ref{theorem-ygc-NIMO}.

>>>>

Our certification techniques are defined generally wrt implementations
of input encoding, decoding, and internal gates for both GMW and YGC
circuits. In the following we will refer to arbitrary decode, encode,
and gate functions with the restriction that any function in each of
these categories has the same valid type signatures as their existing
instantiations in our GMW and YGC libaries. All certifications can be
automatically verified as a consequence of Lemmas \ref{lemma-cprogtt}
and \ref{lemma-autosep}, and complete implementations of the
certifications are available in our repository \cite{jpdf-github},
that we've used to certify our GMW and YGC libraries (Lemmas
\ref{lemma-gmw-certification} and \ref{lemma-ygc-certification}.)

We also demonstrate that properties of certified
components maintain a crucial separation invariant within circuits
using methods developed in Section \ref{section-automation-logic}.
Specifically, we show that within a circuit $\prog$, the views of each
client remain probabilistically independent of the other client's
secrets, i.e., $\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
%\quad \text{and} \quad
$\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$.
Through certification of decodings we can finally obtain $\NIMO$ in
circuits as in Theorems \ref{theorem-gmw-NIMO} and
\ref{theorem-ygc-NIMO}.
